Data Management and Domain Adjusting Strategies for Implementing Parallel SPH Method in JPUE Simulation

### 2016-12-22 Paper for submission.tex
updated the most recent strong scalability test

@@

\includegraphics[scale=0.33]{strong_scale}
\caption{Influence of total work load on strong scalability. It will exceed the time limit on CCR to do a serial simulation for case 2, so the serial simulation time is estimated by assuming that speed up of case 1 and case 2 are the same at 64 processors.}

>>>>

%\includegraphics[scale=0.33]{strong_scale}
%\caption{Influence of total work load on strong scalability. It will exceed the time limit on CCR to do a serial simulation for case 2, so the serial simulation time is estimated by assuming that speed up of case 1 and case 2 are the same at 64 processors.}
%\label{fig:2cases_efficiency}

@@

\subfloat[a]{\includegraphics[scale=0.33]{strong_scale}}
\subfloat[b. zoomed view of a]{\includegraphics[scale=0.33]{strong_scale_zoom}}
\caption{Influence of total work load on strong scalability. Fig. b is the zoomed view of Fig a. It is obviously shown that strong scalability is better when problem size is larger.}
